Dependently Typed Multi-stage Calculus

### 2019-11-29 slides/main.tex
I must blush up from now

\begin{frame}[fragile]{Kinding rules of \LMD}
    Types have also stages because types may contains terms.
    \begin{center}
    {\footnotesize
    \infrule[{\KApp}]{
        \G\V \sigma:: (\Pi x:\tau.K) @ n \andalso \G\V M:\tau @ n
    }{
        \G\V \sigma\ M::K[x\mapsto M] @ n
    }
    \infrule[{\KAbs}]{
        \G\V \tau :: * @ n \andalso \G,x:\tau@ n \V \sigma::J@A
    }{
        \G\V(\Pi x:\tau.\sigma) :: (\Pi x:\tau.J) @ n
    }}
    \end{center}
    So, we need CSP in types also.
    \begin{exampleblock}{}
    \begin{center}
    \( \underbrace{\Pi n:\text{int}. \TW (\overbrace{\text{vec}\ \%n}^{\text{stage }1})}_{\text{stage }0} \)
    \end{center}
    \end{exampleblock}
\end{frame}

>>>>

\begin{frame}[fragile]{Kinding rules of \LMD}
    Kiding judgements also inculde stages.
    \begin{center}
        \( \G \vdash \tau :: K @ n \)
    \end{center}
    Types have also stages because types may contains terms.
    \begin{center}
    {\footnotesize
    \infrule[{\KApp}]{
        \G\V \sigma:: (\Pi x:\tau.K) @ n \andalso \G\V M:\tau @ n
    }{
        \G\V \sigma\ M::K[x\mapsto M] @ n
    }
    \infrule[{\KAbs}]{
        \G\V \tau :: * @ n \andalso \G,x:\tau@ n \V \sigma::J@A
    }{
        \G\V(\Pi x:\tau.\sigma) :: (\Pi x:\tau.J) @ n
    }}
    \end{center}
\end{frame}

\begin{frame}[fragile]{CSP in Types}
    Code type \( \TW \) decreases the stage.
    \begin{center}
        \infrule[{\KTW}]{
            \G\V \tau::*@ n + 1
        }{
            \G\V\TW \tau::*@ n
        }
    \end{center}
    So, we need CSP in types also.
    \begin{exampleblock}{}
        \begin{center}
            \( \underbrace{\Pi n:\text{int}. \TW (\overbrace{\text{vec}\ \%n}^{\text{stage }1})}_{\text{stage }0} \)
        \end{center}
    \end{exampleblock}
\end{frame}
